Fist of all, I would like to thank Prof.~Takayuki Tomaru and Prof.~Nobuyuki Kanda. They support my research activity in Japan not only scientifically but also financially. With their help, I can fully concentrate on my study without worrying about other things. Besides, Dr.~Yuki Inoue, Dr.~Takaaki Yokozawa, and Dr.~Takahiro Yamamoto teach me many practical skills and knowledge during my experiments from the hardware side to the software side. Without their help, it is impossible to get results in this dissertation.

Also, in the last few months, Dr.~Chihiro Kozakai and Dr.~Darkhan Tuyenbayev joined our calibration group. They helped me a lot to dealing with our X-end PCal and perform the measurement with that.

In addition, people in KEK and KAGRA site help me a lot to manage my stay in Japan and help me to go to the site. They are Emiko Kotaki, Ayako Hagiwara, Ayako Ueda, Mihoko Okinaka, Rie Kikuchi, Dr. Takafumi Ushiba, Koki Okutomi, Takahiro Miyamoto and Yutaro Enomoto.

I also want to thank people in KEK cryogenic lab, including Tomohiro Yamada, Takaharu Shishido, Rishabh Bajpai, and, especially, Bin-Hua Hsieh and Kunihiko Hasegawa. Their practical and mental support made my research life indelible.

I want to thank Dr.~Sheau-Shi Pan who teach me how to perform experiments with optics from scratch in ITRI. That is an important experience for me to understand how interferometer works.

At the same time, I really appreciate the strong support from Institute of Physics, Academia Sinica, including Prof.~Chih-Hsun Lin and Prof.~Ming-Lee Chu, who teach me how to make the De-Whitening Filter circuit design. Discussion with them was critical to make this filter become true. Besides, Pei-Rong Tsai, Tracy Liu and Chia-Yi Lee helped me a lot for managing many administrative questions.

I would like to thank Prof.~Rick Savage. He is almost the people who brought me into this field. Even within very limited time, his perception, perseverance,and passion deeply moved me.

Finally and most importantly, I gratefully thank my advisors Prof.~Sadakazu Haino and Prof.~Wolung Lee. They encourage me to have a chance working on hardware development, which I have never thought before but resulting an incredibly useful experience. Their continuous support in any aspect since the first time we met until now fulfill my master course study.

